Merging Datasets Through Deep learning

### 2018-09-05 paper2018/evaluation.tex
adding ref

We therefore compared the hard negative triplet selection mechanism directly to training against semi-hard negatives.  To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that were further from the entity than is the positive.  We made triplets for each such pair of positive and negative.  We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.  We ran experiments again for adapted loss on our people dataset, changing only the training used; these results are in Table~\ref{hard-semi-hard}.  The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.

@@

 The results show training on hard negatives produces consistently better results, both for precision and recall.  Hard negative training resulted in recall of 81\% of positives in the nearest set versus 63\% for semi-hard negatives.  Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.  Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi hard.

\subsection{Generalization Test on Faces}
We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.  We took the two open sourced models \footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Note that for face datasets there is a greater number of variability of faces per identity with a maximum of 529 faces for a single identity.  We adjusted neighborhood length to a maximum of 20 or the number of expected neighbors in our experiments for each face.  Recall was 91\% on the VGGFace2 dataset, and 87\% for the Casia Web Face dataset.  Precision@1 was 95\% for VGGFace2 and 93\% for Casia Web faces.  Overall precision was 91\% for VGGFace2 and Casia Web faces was 87\%.  These results suggest that existing models can in fact be re-purposed for joins.  We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.  The names data had a lot fewer positives per identity.  VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.

\section{Conclusion and Future Work}
We show that deep learning models can be used effectively for joins, and we will provide these models to the community for use.  In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.

>>>>

We therefore compared the hard negative triplet selection mechanism directly to training against semi-hard negatives.  To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that were further from the entity than is the positive.  We made triplets for each such pair of positive and negative.  We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.  We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Table~\ref{hard-semi-hard}.  The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.

@@

 The results show training on hard negatives produces consistently better results, both for precision and recall.  Hard negative training resulted in recall of 81\% of positives in the nearest set versus 63\% for semi-hard negatives.  Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.  Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi-hard.

\subsection{Generalization Test on Faces}
We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:journals/corr/YiLLL14a}.  We took the two open sourced models\footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Note that for face datasets there is a greater number of variability of faces per identity with a maximum of 529 faces for a single identity.  We adjusted neighborhood length to a maximum of 20 or the number of expected neighbors in our experiments for each face.  Recall was 91\% on the VGGFace2 dataset, and 87\% for the Casia Web Face dataset.  Precision@1 was 95\% for VGGFace2 and 93\% for Casia Web faces.  Overall precision was 91\% for VGGFace2 and Casia Web faces was 87\%.  These results suggest that existing models can in fact be re-purposed for joins.  We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.  The names data had a lot fewer positives per identity.  VGGFace2 has 362.6 faces per identity, and in CasiaWebFace, 500,000 images exist for 10,000 identities.

\section{Conclusion and Future Work}
We show that deep learning models can be used effectively for joins, and we provide these models to the community for use.  In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.
